Verifying Spatial Properties of Array Computations

### 2017-04-17 oopsla17/algorithms.tex
Improve on union normal form explanation

We need to address the problem of representation in the model both for observed
array terms converted into subscripts schemes and for specifications converted
into interval schemes. In each case, the objects are sets and union and
intersection are the combinators. However, they are often infinite sets due to
infinite interval and constant indices being converted to \bz{}. This calls for
a finite (and ideally compact) representation for indices.

First recall \Cref{lem:vector-intersect}, which states that intersection of
indexing schemes is still an indexing scheme. When combined with
\Cref{lem:interval-identities}, we can extend this closure to interval schemes.
Subscripts schemes do not enjoy the same propery as intersection of two
singleton sets might easily be empty, which disqualifies it from being a
subscript index. In the following section we will not rely on intersection of
subscript indices, so that is okay.

Union is, however, not as flexible as intersection. \Cref{lem:vector-union} does
not form a closure for indexing schemes in general. For this reason, we
represent collection of all forms of indexing schemes as unevaluated unions.
Since the model forms a distributive lattice as established in
\Cref{prop:region-lattice}, the intersections can be pushed in using the
distributive law leaving only unions. We further exploit associativity of union
to put unions into a cons tree making the unions effectively a non-empty list.
We do not, however, attempt to canonicalise the representation.

>>>>

We need to address the problem of representation in the model for index schemes.
In each case, the objects are sets and union and intersection are the
combinators. However, they are often infinite sets due to \bz{} in Cartesian
product. This happens when constant indices of array terms are converted to
\bz{} in subscript schemes and when infinite interval is generated in interval
schemes. This calls for a finite (and ideally compact) representation for
indices.

First recall \Cref{lem:vector-intersect}, which states that intersection of
indexing schemes is still an indexing scheme. When combined with
\Cref{lem:interval-identities}, we can extend this closure to interval schemes.
Subscripts schemes do not enjoy the same propery as intersection of two
singleton sets might easily be empty, which disqualifies it from being a
subscript index. In the following sections we will not rely on intersection of
subscript indices, so that is not a problem.

Union, however, is not as flexible as intersection. \Cref{lem:vector-union} does
not form a closure for indexing schemes in general. For this reason, we
represent collection of all forms of indexing schemes as unevaluated unions.
Since the model forms a distributive lattice as established in
\Cref{prop:region-lattice}, the intersections can be pushed in using the
distributive law leaving only unions. We further exploit associativity of union
to put unions into a cons tree making the unions effectively a non-empty list.
We do not, however, attempt to canonicalise the representation. Later on
\Cref{lem:vector-union} and index scheme subset are used to reduce the size of
union normal form.
